HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-15 scnn.tex
first draft of architecture subsection

% MATH SYMBOLS
\newcommand{\1}{\b{1}}              % all-ones vector
\newcommand{\0}{\b{0}}              % all-zero vector
\newcommand{\g}[1]{\b{#1}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\E}{\mathcal{E}}
\renewcommand{\L}{\b{L}}
\newcommand{\tL}{\tilde{\L}}
\newcommand{\W}{\b{W}}
\newcommand{\I}{\b{I}}
\newcommand{\D}{\b{D}}
\newcommand{\U}{\b{U}}
\newcommand{\x}{\b{x}}
\newcommand{\bu}{\b{u}}
\newcommand{\f}{\b{f}}
\newcommand{\trans}{^\intercal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bLambda}{\b{\Lambda}}
\newcommand{\blambda}{\b{\lambda}}
\newcommand{\bO}{\mathcal{O}}
\newcommand{\pkg}[1]{\texttt{#1}}

@@

To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling. The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which is efficient and can adapt to any sampling of the sphere. Using a k-nearest neigboors graph, the convolution operation costs $\mathcal{O}(n)$ operations, where $n$ is the number of pixels. This is the lowest possible complexity for a convolution operation without approximations (e.g. by sketching).
The flexibility of modeling the data domain with a graph allows, for example, to easily model data which only spans a part of the sphere, or data which is not uniformly sampled.
Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales.
Such hierarchical pixelizations of the sphere have been well studied.

@@

We will hence make a detour by the spectrum to perform the convolution.\footnote{Note that we only use the spectrum to define the convolution. The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
The gist of our method is to define the convolution on a sphere using a graph, and the down-sampling using a hierarchical pixelization of the sphere.
This contribution leverages the emerging field of graph signal processing~\citep{shuman2013emerging} which defines fundamental signal processing tools such as the Fourier transform for signals defined on graphs.

@@

\subsection{Architecture}
\label{sec:architecture}

Now that all the building blocks are defined, let's discuss our proposed spherical CNN architecture, pictured in \figref{architecture}.

\todo{present and discuss the whole CNN architecture.}

Learning the $\theta_k$.

>>>>

% MATH SYMBOLS
\newcommand{\1}{\b{1}}              % all-ones vector
\newcommand{\0}{\b{0}}              % all-zero vector
\newcommand{\g}[1]{\b{#1}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\E}{\mathcal{E}}
\renewcommand{\L}{\b{L}}
\newcommand{\tL}{\tilde{\L}}
\newcommand{\W}{\b{W}}
\newcommand{\I}{\b{I}}
\newcommand{\D}{\b{D}}
\newcommand{\U}{\b{U}}
\newcommand{\x}{\b{x}}
\newcommand{\X}{\b{X}}
\newcommand{\y}{\b{y}}
\newcommand{\Y}{\b{Y}}
\newcommand{\bu}{\b{u}}
\newcommand{\f}{\b{f}}
\newcommand{\trans}{^\intercal}
\newcommand{\R}{\mathbb{R}}
\newcommand{\bLambda}{\b{\Lambda}}
\newcommand{\blambda}{\b{\lambda}}
\newcommand{\bO}{\mathcal{O}}
\newcommand{\pkg}[1]{\texttt{#1}}

@@

To overcome those shortcomings, we introduce an efficient spherical CNN formulation which uses (i) convolutions on graphs and (ii) hierarchical pooling. The main idea is to represent the sphere $S^2$, a 2-dimensional manifold embedded in $\mathbb{R}^3$, as a graph of connected pixels.
This contribution leverages the emerging field of graph signal processing which defines fundamental signal processing tools such as the Fourier transform for signals defined on graphs \citep{shuman2013emerging}.
Our approach uses the graph CNN formulation introduced by \citet{defferrard2016convolutional}, which is efficient and can adapt to any sampling of the sphere. Using a $k$-nearest neighbors graph, the convolution operation costs $\mathcal{O}(N_{pix})$ operations, where $N_{pix}$ is the number of pixels. This is the lowest possible complexity for a convolution operation without approximations (e.g. by sketching).
The flexibility of modeling the data domain with a graph allows, for example, to easily model data which only spans a part of the sphere, or data which is not uniformly sampled.
Our hierarchical pooling strategy exploits a hierarchical pixelization of the manifold to analyze the data at multiple scales.
Such hierarchical pixelizations of the sphere have been well studied.

@@

We will hence make a detour by the spectrum to perform the convolution.\footnote{Note that we only use the spectrum to define the convolution. The implementation however does not need a direct access to the spectrum, which is computationally much more efficient. See \secref{efficient_convolution}.}
The gist of our method is to define the convolution on a sphere using a graph, and the down-sampling using a hierarchical pixelization of the sphere.

@@

\subsection{Graph convolutional neural network}
\label{sec:architecture}

A typical neural network is constructed as a stack of layers, which sequentially transform the input data. Our architecture, pictured in \figref{architecture}, is composed of the following types of layers: graph convolutional (GC) layers, non-linearity, pooling (P), batch normalization (BN), and fully connected (FC) layers. All GC and FC layers are always followed by a non-linearity. As such, we will not mention the non-linearity in the description of our architectures.

A GC layer takes as input a data matrix $\X = [\x_1, \ldots, \x_{F_{in}}] \in \R^{N_{pix} \times F_{in}}$ and outputs a data matrix $\Y = [\y_1, \ldots, \y_{F_{out}}] \in \R^{N_{pix} \times F_{out}}$, where $N_{pix}$ is the number of pixels and nodes, $F_{in}$ is the number of input features, and $F_{out}$ is the number of output features. Each output feature map $\y_i \in \R^{N_{pix}}$ is computed by
\begin{equation*}
	\y_i = \sum_{j=1}^{F_{in}} h_{\theta_{ij}}(\tL) \x_j.
\end{equation*}
As such, a GC layer is composed of $F_{in} \cdot F_{out}$ filters, each parameterized by $K$ numbers. All those parameters are learned during training via back-propagation of the error gradient.

A FC layer takes as input $\x \in \R^{F_{in}}$ and outputs $\y \in \R^{F_{out}}$ as
\begin{equation*}
	\y = \b W \x,
\end{equation*}
where $\W \in \R^{F_{out} \times F_{in}}$ is the parameter matrix that is learned.
Note that the output $\Y \in \R^{N_{pix} \times F_{out}}$ of the last GC is vectorized as $\x \in \R^{F_{in}}$ before being fed to the first FC, where $F_{in} = N_{pix} \cdot F_{out}$.

GC32 - P256 - FC10

The whole network is then optimized to minimize the loss function over the training data.
Describe the loss function.
